\vspace{50pt}\\ \huge \bfseries SKEDGE \\ \vspace{10pt} \Large Smarter course scheduling for our\\ University of Rochester

### 2016-04-12 analytics.tex
Remove unneeded files
Analytics work

\chapter{Data Analytics}

Hypotheses:

1. Skedge's differences from and additions to CDCS are usable and have real need

2. Skedge’s navigations-per-add and other metrics demonstrate effectiveness of the use cases
a) direct searching, and
b) course browsing

3. Skedge’s DSL is user-friendly; users learn more advanced search types over time by using it

@@

Since November 3rd 2015 (137 days)
3,768 unique users
4,500 schedules
Average 90 sessions/day
Average 4.92 pages/session
Average 5:31 minutes/session
28\% of sessions are from new users

MOBILE RESULT

@@

% figs

@@

\subsection{Course blocks}

40\% of sessions have at least one block-click
Average of 4.94 block-clicks per session

\subsection{Social}

\subsection{Conclusion}

Success! Considering skedge is OPTIONAL.
+ course blocks (obv usecase, can't click)
+ exports (not supported by thing)
+ mobile

\section{Navigations-per-add}

@@

The navigations-per-{add, bookmark} measure is
the number of navigations a user took (within one session) until a course was {added, bookmarked}

@@

%figs

@@

@@

\subsection{Conclusion}

%figs

@@

\section{Users' search types over time}

@@

% fig

First increase (60.5% of users)
Median: 2 searches
Average: 4.23 searches
(Starting at 1 counts as an increase value of 0)

Second increase (7.9% of users)
Median: 8 searches
Average: 17.52 searches

\subsection{Conclusion}

DSL++

>>>>

\chapter{Data analytics}

In this chapter I propose three hypotheses. They are:

\begin{enumerate}
  \item Skedge's differences from and additions to CDCS are \textbf{usable and have real need}.

  \item Skedge’s \emph{navigations-per-add} demonstrate the \textbf{effectiveness of its search features} for each of the following three user search paradigms:

  \begin{enumerate}
    \item direct search,
    \item exploratory search, and
    \item peer-guided search
  \end{enumerate}

  \item Skedge’s \textbf{DSQL is user-friendly}; users learn more advanced search types over time \textbf{simply by using it}.
\end{enumerate}

\noindent In the following sections I will present my analysis on collected usage data since November 3rd 2015, which will serve to validate each hypothesis.

@@

From November 3, 2015 to April 11, 2016 (a period of 159 days), Skedge has seen\ldots

\begin{itemize}
  \item 4,713 users that have added or bookmarked at least 1 course
  \item 5,256 schedules
  \item 17,012 sessions\footnote{A session is defined by a period of activity expiring after 30 minutes of inactivity}, 75\% of which are from returning visitors
  \item 107 sessions per day, on average
  \item 5.40 pages viewed per session, on average 
  \item 6 minutes spent per session, on average
\end{itemize}

\begin{figure}
  \centering

  \includegraphics[width=1.0\textwidth]{images/graph/searches}

  \caption{Etc}
  \label{fig:searches}

\end{figure}

periodic visit cycle graph means people are actually using it and decided to stay with it, not declining, can be seen w exports & link-searches.

also should be noted that NO seniors participated in the last, the majority of the userbase!

success Considering skedge is OPTIONAL.

\subsection{Exports}

\begin{figure}
  \centering
  \includegraphics[width=1.0\textwidth]{images/graph/exports}

  \caption{Etc}
  \label{fig:searchtypes}
\end{figure}

Success! (broken on cdcs)

\subsection{``Link-searches''}

\begin{figure}
  \centering
  \includegraphics[width=1.0\textwidth]{images/graph/linksearches}

  \caption{Etc}
  \label{fig:searchtypes}
\end{figure}

Success, used!

\subsection{Mobile}

\begin{itemize}
  \item 11.54\% of sessions
  \item 2.74 page viewed per session, on average
  \item 2 minutes spent per session, on average
\end{itemize}

success bc mobile doesn't exist on cdcs

\subsection{Course Blocks}

\begin{figure}
  \centering

  \fbox {
    \includegraphics[width=8cm]{images/skedge/blocks}
  }

  \caption{Etc}
  \label{fig:searchtypes}

\end{figure}

40\% of sessions have at least one block-click
Average of 5.12 block-clicks per session

success because you can't click schedule blocks in better cdcs!!

@@

  \subsubsection{Search types}

  \begin{figure}
    \centering
    \includegraphics[width=1.0\textwidth]{images/graph/searchtypes}

    \caption{Etc}
    \label{fig:searchtypes}

  \end{figure}

@@

\section{Effectiveness of search}

@@

The navigations-per-add measure is
the number of navigations a user took (within one session) until a course was added, bookmarked

@@

\begin{figure}
  \centering
  \includegraphics[width=1.0\textwidth]{images/graph/combined_navs}

  \caption{Etc}
  \label{fig:searchtypes}
\end{figure}

@@

  \begin{figure}
    \centering
    \includegraphics[width=1.0\textwidth]{images/graph/direct_navs}

    \caption{Etc}
    \label{fig:searchtypes}
  \end{figure}

  Why would 0-navs be so common with direct searches? 65\% subsections!

@@

  \begin{figure}
    \centering
    \includegraphics[width=1.0\textwidth]{images/graph/browse_navs}

    \caption{Etc}
    \label{fig:searchtypes}
  \end{figure}

  As expected, the 0-navs were mostly maincourses

@@

  \subsubsection{Social}

  success?????

\section{Complexity of users' searches over time}

@@

\begin{figure}
  \centering

  \includegraphics[width=1.00\textwidth]{images/graph/search_dt}

  \\
  \vspace{5pt}

  \includegraphics[width=0.65\textwidth]{images/table/search_dt}

  \caption{Etc}
  \label{fig:searchtypes}
\end{figure}

First increase (60.5\% of users)
Median: 2 searches
Average: 4.23 searches
(Starting at 1 counts as an increase value of 0)

Second increase (7.9\% of users)
Median: 8 searches
Average: 17.52 searches

DSQL++

### 2016-04-12 tech.tex
More design
work on social... so slow
Small fixes
Analytics work

\section{Back-end}

Skedge's infrastructure is built

\emph{nginx}, \emph{unicorn}, \emph{Ruby on Rails}, \emph{PostgreSQL}, \emph{React.js}, \emph{Ahoy}, and Google Analytics.

\section{Front-end}

\section{Analytics}

>>>>

\section{Architecture}

\emph{nginx}, \emph{unicorn}, \emph{Ruby on Rails}, \emph{PostgreSQL}, \emph{React.js},

\section{Data storage}

cookies, likes not on fb

\section{Usage data collection}

As the saying goes, ``if it's not monitored, it's not in production'' \cite{monitored} (how else would we know that it was?) anonymous, \emph{Ahoy} and Google Analytics.
